---
title: "cgdsr"
output: html_document
---

## connection

the first thing you need to do is create a connection, then test it.

```{r}
library(cgdsr)
mycgds <- CGDS("http://www.cbioportal.org/public-portal/")
test(mycgds)
```

## pick one project

the function `getCancerStudies` will return all available cancer studies, the output is a data.matrix, contains cancer_study_id, name and description; here, i use the project: Breast Cancer (METABRIC, Nature 2012 & Nat Commun 2016)

```{r }
all_cancerstudy <- getCancerStudies(mycgds)
all_cancerstudy[1:10, 1:2]

mycancerstudy <- all_cancerstudy[19, 1]
```

## case

one project may contain many cases, for example, the project "brca_metabric" contain six caselist:

```{r}
all_caselist <- getCaseLists(mycgds, mycancerstudy)
all_caselist[, 1:2]
mycaselist <- all_caselist[1,1]
```

## data

the brca_metabric study have more than one genetic profiles: 

```{r}
all_geneticprofile <- getGeneticProfiles(mycgds, mycancerstudy)
all_geneticprofile[, 1:2]
mygeneticprofile <- all_geneticprofile[4,1]
```

## Clinical Data 

[Clinical Data](http://www.cbioportal.org/study?id=brca_metabric#clinical) on the web

```{r}
myclinicaldata <- getClinicalData(mycgds, mycaselist)
colnames(myclinicaldata)
```

## do analysis

now, simple analysis

```{r}
boxplot(TUMOR_SIZE ~ COHORT, data = myclinicaldata,
        xlab = "COHORT", ylab = "TUMOR_SIZE")
```

## other
```{r}
x = getMutationData(mycgds, mycaselist, mygeneticprofile, c('BRCA1','BRCA2'))
y = getProfileData(mycgds, c('BRCA1','BRCA2'), mygeneticprofile, mycaselist)
```


## download 

or, you can download all data from [github](https://media.githubusercontent.com/media/cBioPortal/datahub/master/public/brca_metabric.tar.gz)